OwO

### 2020-05-18 4-Object-detection.tex
Add new stuff to object detection

>>>>

\section{Metrics}
The training of object detection models requires data sets that have been labeled for that purpose.
Generally, the data sets contain bounding box annotations for each of the classes in the data set, such as seen in Figure 5.1.
For this reason, object detection models can't use a simple metric like the basic accuracy in image classification.
As the images are often manually labeled, the boxes are most likely not completely consistent.
So most likely, the predictions are never going to align with the labeled boxes perfectly.
Consequently, the method for evaluating object detection performance is Average Precision (AP) or mean Average Precision (mAP) or one of their variants.
These metrics use intersection over union (IoU) score to evaluate how incorrect the predicted bounding box is when compared to the actual label. Intersection over union is visualized in Figure 5.1.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{imgs/intersection_over_union.png}
    \caption{The visual formula for calculating intersection over union.}
\end{figure}

To get to a final AP score, the first thing that has to be decided is the IoU score threshold for considering a prediction to be correct.
For example, we could consider all predictions that have over 50\% or 75\% overlap in the IoU.
The threshold value for IoU that should be used is not entirely standardized, and there are multiple ways of calculating the AP score.
For example, the popular COCO dataset \citep{COCO} uses an average of 10 IoU scores ranging from .5 to .95 IoU thresholds as the main metric.
To get the AP for a class, we need to graph the precision-recall curve and then calculate the area under it.
For example, the Pascal Visual Object Classes Challenge (VOC) \citep{PVOC} recommends doing this by using 11 points of interpolated precision.
So we get the following formula for Average Precision:

\[AP = \frac{1} {11} L_{total} = \sum_{r \in \{0, 0.1, \ldots, 0.9 , 1\}}{p_{interp}(r)}\] \noindent

Where $p_{interp}$ is defined as

\[p_{interp}(r) = \max \limits_{\tilde{r}:\tilde{r} \geq r} p(\tilde{r})\]

Then to get the mAP score, we can average the AP score for each of the classes in the data set.
As was mentioned, this way of calculating the AP is not always the same, for example, the COCO metrics \citep{COCO_SITE} recommend using 101 points for integrating the curve instead of the 11 proposed in the VOC.
This discrepancy in the integration means that not all AP scores are directly comparable.

\section{Multi-dataset training}
Often an object detection problem requires detecting multiple different classes in a similar context.
For example, a self-driving car would need to detect various traffic signs, cars, pedestrians, road markings, cyclists, and many other things.
Collecting a single dataset that has labels for all of the classes of interest can be a very daunting task.
Even if it is feasible to create the dataset for the original classes of interest, this approach does not scale very well when new classes need to be recognized.
As likely the original dataset might contain millions of images labeled for multiple classes, adding a new class would require going through the entire dataset again and labeling the new class as well.
The new class may be relatively rare; for example, we may be interested in detecting emergency vehicles with sirens on.
Here is where multi-dataset learning is highly beneficial as it only allows for collecting a specific class dataset.
This type of cross-dataset learning is useful when we need to combine multiple distinct data sources to detect some union of the labels \citep{cross_data}.

The main difficulty in combining multiple datasets for detection lies in the fact that they likely contain unlabeled overlapping classes.
For example, given a dataset for detecting cars and another for detecting stop signs, we have two distinct datasets where only one of the classes is labeled.
If we train this model, assuming that the labels are genuinely valid, we will end up unlearning the tasks due to the overlap of the classes.
The problem lies in the fact that it is most likely that in the car dataset, we will find stop signs that are not labeled.
Similarily we will find cars that are unlabeled within the stop sign dataset.
When we naively train this model, we will end up detecting cars and stop signs that are actually correct but incorrect based on the labels.
The model will be punished for detecting these non-labeled positive examples due to the absence of the labels.

Similar multi-dataset training can also be applied in multi-label image classification settings.
A multi-label image classification problem is one where we want to assign multiple labels to an image.
For example, we might want to classify whether it is raining, the sun is shining, the sea is visible, is there a dog in the image, and so on for all the classes of interest.
Again, collecting a dataset containing all labels for all images is quite expensive, but we can train this with a separate binary classification head for each task.
And as collecting a separate dataset for each task is relatively easy, it is possible to create a quite powerful model with relative ease.

\section{Self-supervised object detection}

\section{EfficientDet}

### 2020-05-18 7-Experiments.tex
Add new stuff to object detection

\section{Different tasks using shared representation}
Here we will create similar models to \citep{visualPerson}, but using EfficientNet, and then we will add a shared object detector to detect the people.

\section{Multiple object detectors}
Train multiple object detector using shared representations

>>>>

\section{Object detection with image classification}
Okay coolio

\section{Object detection classification and segmentation}
Train cool stuff
